---
title: "DS400: Assignment V (R)"
author: "Simon Andres (Student ID: 4148078)"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    self_contained: true
---

```{r setup, include = F}
options(scipen=999)
```

***

### GitHub repository

(1) - (4) The GitHub setup was done, all steps of this project are documented in my repository, follow this link: https://github.com/Studymon/DSPM_Assignment5


***

### Getting to know the API

<div class="alert alert-block alert-info">
5. Visit the documentation website for the API provided by ticketmaster.com. Familiarize yourself
with the features and functionalities of the Ticketmaster *Discovery* API. Have a particular look at
rate limits.
</div>

<div class="alert alert-block alert-info">
6. Whithin the scope of this assignment, you do **not** have to request your own API key. Instead retrieve
a valid key from the API Explorer. This API key enables you to perform the `GET` requests needed
throughout this assignment. Even though this API key is not secret per se (it is publicly visible on the
API Explorer website), please comply to the common secrecy practices discussed in the lecture and the
tutorial: Treat the API key as a **secret** token. Your API key should neither appear in the code that you
are submitting nor in your public GitHub repository.
</div>


***

### Interacting with the API - the basics

<div class="alert alert-block alert-info">
7. Perform a first `GET` request, that searches for event venues in Germany (`countryCode = "DE"`). Extract
the `content` from the `response` object and inspect the resulting list. Describe what you can see.
</div>

```{r}
# Preparation
rm(list = ls())
```


```{r}

```

<div class="alert alert-block alert-info">
8. Extract the `name`, the `city`, the `postalCode` and `address`, as well as the `url` and the `longitude`
and `latitude` of the venues to a data frame.
</div>

```{r}

```

***

### Interacting with the API - advanced

<div class="alert alert-block alert-info">
9. 
</div>

```{r}

```

***

### Visualizing the extracted data

<div class="alert alert-block alert-info">
10. 
</div>

```{r}

```

***

### Event locations in other countries

<div class="alert alert-block alert-info">
12. Repeat exercises (9) - (11) for another European country of your choice.
</div>

```{r}

```
