---
title: "DS400: Assignment V (R)"
author: "Simon Andres (Student ID: 4148078)"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    self_contained: true
---

```{r setup, include = F}
options(scipen=999)
```

***

### GitHub repository

(1) - (4) The GitHub setup was done, all steps of this project are documented in my repository, follow this link: https://github.com/Studymon/DSPM_Assignment5


***

### Getting to know the API

<div class="alert alert-block alert-info">
5. Visit the documentation website for the API provided by ticketmaster.com. Familiarize yourself
with the features and functionalities of the Ticketmaster *Discovery* API. Have a particular look at
rate limits.
</div>

I made myself familiar with the Ticketmaster Discovery API and understand that there is a rate limit of max. 5 requests per second and a maximum number of daily requests of 5000.


<div class="alert alert-block alert-info">
6. Within the scope of this assignment, you do **not** have to request your own API key. Instead retrieve
a valid key from the API Explorer. This API key enables you to perform the `GET` requests needed
throughout this assignment. Even though this API key is not secret per se (it is publicly visible on the
API Explorer website), please comply to the common secrecy practices discussed in the lecture and the
tutorial: Treat the API key as a **secret** token. Your API key should neither appear in the code that you
are submitting nor in your public GitHub repository.
</div>

To comply with the common secrecy practices, the key was stored in a separate script that is stored in a subfolder `api_keys` excluded from syncing with the GitHub repository through the .gitignore file.

```{r, warning = FALSE, message = FALSE}
# Preparation
rm(list = ls())

# Libraries
library(jsonlite)
library(httr)
library(rlist)
library(tidyverse)
```

```{r}
# source the ticketmaster key from separate script
source("./api_keys/tm_key.R")
```

***

### Interacting with the API - the basics

<div class="alert alert-block alert-info">
7. Perform a first `GET` request, that searches for event venues in Germany (`countryCode = "DE"`). Extract
the `content` from the `response` object and inspect the resulting list. Describe what you can see.
</div>

```{r}
# make request
firstVenues <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                     query = list(
                        apikey = tm_key,
                       "countryCode" = "DE",
                       "locale" = "*")
                   )

# make unicode readable
firstVenues <- content(firstVenues)

# the first 20 results (first page) are stored in the "venues" list within the
# "_embedded" list of the content
summary(firstVenues)
```

Our request from the ticketmaster API contains three lists: `_embedded`, `_links`, and `page`

```{r}
# first, we'll look at the page structure
firstVenues[["page"]]
```

We see that for our request there is a total of 12934 elements. However, our specific request only yields the first 20 results, as that is the default number of search results per page for the ticketmaster API. Thus, there are 647 pages in total. The first page index is zero.

```{r}
summary(firstVenues[["_embedded"]])
```

We see that the list `_embedded` contains the list `venues`, which contains information about a total of 20 venues as expected

```{r}
# looking at what information we get on the first element
str(firstVenues[["_embedded"]][["venues"]][[1]])
```

We see that for the first result, we get information on multiple properties of the venue: Name, type, ID, ...
Some of this information is stored in strings, some of it is stored in further sublists.


<div class="alert alert-block alert-info">
8. Extract the `name`, the `city`, the `postalCode` and `address`, as well as the `url` and the `longitude`
and `latitude` of the venues to a data frame.
</div>

```{r}
# looking at the structure above, we see how to access each of these elements

# store number of results per page in n_perPage
n_perPage <- firstVenues[["page"]]$size

# initiate df
firstVenues_df <- tibble(
  name = character(n_perPage),
  city = character(n_perPage),
  postalCode = double(n_perPage),
  address = character(n_perPage),
  url = character(n_perPage),
  longitude = double(n_perPage),
  latitude = double(n_perPage),
)

# retrieve information by iterating over all entries of page
for (i in 1:n_perPage){
  # name
  firstVenues_df[i,1] <- firstVenues[["_embedded"]][["venues"]][[i]]$name
  # city
  firstVenues_df[i,2] <- firstVenues[["_embedded"]][["venues"]][[i]]$city %>% unlist()
  # postal code
  firstVenues_df[i,3] <- firstVenues[["_embedded"]][["venues"]][[i]]$postalCode %>% as.double()
  # address
  firstVenues_df[i,4] <- firstVenues[["_embedded"]][["venues"]][[i]]$address %>% unlist()
  # url
  firstVenues_df[i,5] <- firstVenues[["_embedded"]][["venues"]][[i]]$url
  # longitude
  firstVenues_df[i,6] <- firstVenues[["_embedded"]][["venues"]][[i]]$location$longitude %>% as.double()
  # latitude
  firstVenues_df[i,7] <- firstVenues[["_embedded"]][["venues"]][[i]]$location$latitude %>% as.double()
}

as.data.frame(t(firstVenues_df))

```

&rarr; The dataframe looks as intended. There is one row for each entry (i.e. each venue), so 20 in total, and 7 columns for the venue properties we wanted to extract. Note that (only for displaying the data frame here) it was transposed.

***

### Interacting with the API - advanced

<div class="alert alert-block alert-info">
9. Have a closer look at the list element named `page`. Did your `GET` request from exercise (7) return *all*
event locations in Germany? Obviously not - there are of course much more venues in Germany than
those contained in this list. Your `GET` request only yielded the first results page containing the first
20 out of several thousands of venues. Check the API documentation under the section *Venue Search*.
How can you request the venues from the remaining results pages? Iterate over the results pages and
perform `GET` requests for all venues in Germany. After each iteration, extract the seven variables `name`,
`city`, `postalCode`, `address`, `url`, `longitude`, and `latitude`. Join the information in one large
data frame. Print the first 10 rows and the shape of the resulting data frame.
</div>

```{r}
# make first request
firstVenues <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                     query = list(
                        apikey = tm_key,
                       "countryCode" = "DE",
                       "locale" = "*",
                       "page" = 177)
                   )

# make unicode readable
firstVenues <- content(firstVenues)

# store number of total results in n
n <- firstVenues[["page"]]$totalElements

# store number of pages in n_pages
n_pages <- firstVenues[["page"]]$totalPages

# initiate df collecting all venues in Germany
venuesGER <- tibble(
  name = character(n),
  city = character(n),
  postalCode = double(n),
  address = character(n),
  url = character(n),
  longitude = double(n),
  latitude = double(n),
)

x = 1
faultyPages <- 0

# Loop
for (i in 1:n_pages) {
  
  # enforce rate limit
  Sys.sleep(0.2)
  
  # store results of each page temporarily
  tempResults <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                     query = list(
                        apikey = tm_key,
                       "countryCode" = "DE",
                       "locale" = "*",
                       "page" = i-1)
                   )
  # check the status code
  if (status_code(tempResults) != 200) {
    
    # adjust current row in df, add to faultyPages counter
    x <- x + 1
    faultyPages <- faultyPages + 1
    
    # skip the current iteration of the for loop
    next
  }
  
  tempResults <- content(tempResults)
  
  for (j in 1:tempResults[["page"]]$size) {
    # name
    venuesGER[x,1] <- tempResults[["_embedded"]][["venues"]][[j]]$name
    # city
    venuesGER[x,2] <-
      ifelse("city" %in% names(tempResults[["_embedded"]][["venues"]][[j]]),
             tempResults[["_embedded"]][["venues"]][[j]]$city %>% unlist(),
             NA) 
    # postal code (missing for some --> NA)
    venuesGER[x,3] <-
      ifelse("postalCode" %in% names(tempResults[["_embedded"]][["venues"]][[j]]),
             tempResults[["_embedded"]][["venues"]][[j]]$postalCode %>% as.double(),
             NA)    
    # address (missing for some --> NA)
    venuesGER[x,4] <-
      ifelse("address" %in% names(tempResults[["_embedded"]][["venues"]][[j]]),
             tempResults[["_embedded"]][["venues"]][[j]]$address %>% unlist(),
             NA)
    # url
    venuesGER[x,5] <- tempResults[["_embedded"]][["venues"]][[j]]$url
    
    # longitude and latitude is missing for many venues, so give NA accordingly
    if("location" %in% names(tempResults[["_embedded"]][["venues"]][[j]])) {
      venuesGER[x,6] <- tempResults[["_embedded"]][["venues"]][[j]]$location$longitude %>% as.double()
      venuesGER[x,7] <- tempResults[["_embedded"]][["venues"]][[j]]$location$latitude %>% as.double() 
    } 
    else {
      venuesGER[x,6] <- NA
      venuesGER[x,7] <- NA
    }
    
    # jump to next row in results df
    x = x + 1
  }
  
}
```


***

### Visualizing the extracted data

<div class="alert alert-block alert-info">
10. 
</div>

```{r}

```

***

### Event locations in other countries

<div class="alert alert-block alert-info">
12. Repeat exercises (9) - (11) for another European country of your choice.
</div>

```{r}

```
